---
runtime: shiny
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(shiny)
source("global/helpers.R")
```

## Try(code, session)
If you enclose a block of code in `Try` block, the warning messages 
and error messages will be output to browser as notifications.

```{r}
# UI code
# UI code
tagList(
  textInput("age1", "try enter your actual age, 0, and some text like 
            \"secret\", or a negative age"),
  actionButton("submit", "Submit")
)

# Server code for exception handling
observeEvent(input$submit, {
  Try({
    if (isolate(input$age1) == "")
      stop("You must input an age!")
    age <- strtoi(isolate(input$age1))
    if (is.na(age) || age < 0)
      stop("age must be a positive integer")
    if (age == 0)
      warning("Really!? You were born to know how to use computer?")
    sendSuccessMessage(session, paste("Your age is", age))
  }, session)
})
```

<br />
<br />

## Put Validator in Try
It is quite often that we need to validate similar things in many different block.
It would be cumbersome and error-prone if we were to write the validation each time. So
we will just write a function called `validate`, and call tihs function at the beginning
of our `Try` block everytime.

```{r}
# UI code
tagList(
  textInput("age2", "try enter your actual age, 0, and some text like 
            \"secret\", or a negative age"),
  fluidRow(
    column(6, actionButton("drive", "Can I Drive?")),
    column(6, actionButton("beer", "Can I Get a Beer?"))
  )
)

# Server code for exception handling
validator <- function(input) {
  if (isolate(input$age2) == "")
    stop("You must input an age!")
  age <- strtoi(isolate(input$age2))
  if (is.na(age) || age < 0)
    stop("age must be a positive integer")
  if (age == 0)
    warning("Really!? You were born to know how to use computer?")
}

observeEvent(input$drive, {
  Try({
    validator(input)
    if (input$age2 >= 16)
      sendSuccessMessage(session, "Yes, go get your liscence!")
    else
      sendErrorMessage(session, "No, Wait until you are 16!")
  }, session)
})

observeEvent(input$beer, {
  Try({
    validator(input)
    if (input$age2 >= 21)
      sendSuccessMessage(session, "Yes, go get a Corona!")
    else
      sendErrorMessage(session, "Sorry, in US, you gotta be at least 21 to drink")
  }, session)
})
```
