---
title: "File Organization"
runtime: shiny
output: html_document
---

```
|-- .Database       # .Database and data related to database operation
|-- data            # folder should not be modified manually
|-- README.md       # this file
|-- WWW             # folders for network resources
|---|-- css         # all css files
|---|-- js          # all javascript files
|-- global          # folders for all global data
|---|-- constants.R # all global constants
|---|-- database.R  # database class
|---|-- help.R      # all help message
|---|-- helpers.R   # all helper functions
|---|-- messagess.R # all warning/error messages
|---|-- study.R     # study class
|-- global.R        # Shiny's env setup file, will be
|                   # executed before app start up
|-- server          # folder for all server modules
|---|-- ...
|-- server.R        # Shiny's default server file
|-- ui              # folder for all ui modules
|---|-- ...
|-- ui.R            # Shiny's default ui file
```

## The Constants

### global.R
* All variables declared in `global.R` is visable globally
* This file is load before shiny app start up, so it is reponsible for sourcing all other constants file and set up the environment (set up database for example)

### constant.R
* `global/constants.R` is where one would store progeam related contant.
* parameter options should be stores in this file

### message.R
* `global/messages.R` is where all error and warning messages are declared,
* All variable name in this file start with `MSG.`, for example:
```{r eval=FALSE}
MSG.merge.noname <- "Study Name can not be empty"
```

### help.R
* `global/help.R` is where all help messages are declared.
* All variable name in this file starts with `HELP.`, for example,
```{r eval=FALSE}
HELP.delete <- "are u sure you want to delete the files?"
```
* help message can be in html format.
* All help messages in `global/help.R` should not contain newline character. If you really want to format the message, use `paste`:
```{r eval=FALSE}
Help.replicate <- paste(
  "Handing replicated gene symbol (replicated row names of your dataset)",
    "<ul>",
      "<li> IQR: </li>",
      "<li> largest: </li>",
      "<li> average: </li>",
    "</ul>"
)
```

