---
title: "Developer"
runtime: shiny
output: html_document
---

## Helpers
### sendErrorMessage(session, msg) 
`sendErrorMessage` will send a warning message to the browser, it should be used in `server.R` or server modules. Alternatively, we have `sendWarningMessage(session, msg)` and `sendSuccessMessage(session, msg)`
```{r}
tagList(
  textInput('message', 'Enter your message', 'this is a message'),
  actionButton('errorMessage', 'Send Error Message', class="btn-danger"),
  actionButton('warningMessage', 'Send Warning Message', class="btn-warning"),
  actionButton('successMessage', 'Send Success Message', class="btn-success")
)

# Server code for sending messages
observeEvent(input$errorMessage, {sendErrorMessage(session, input$message)})
observeEvent(input$warningMessage, {sendWarningMessage(session, input$message)})
observeEvent(input$successMessage, {sendSuccessMessage(session, input$message)})
```

### helpIcon(id, msg)
`helpIcon(id, msg)` will create a UI component that displays `msg` when mouse is hovered. 
Always put the definition of the message in `global/help.R` file, never enter message 
diectly. See [File Organization](file.Rmd) for more information about help message 
definition.
```{r}
tagList( h4("Annotation"), helpIcon("annotate_help", HELP.annotate))
tagList( h4("Delete"), helpIcon("delete_help", HELP.delete))
```
