---
title: "metaOmics"
runtime: shiny
output: html_document
---

A graphical user interface to facilitate the application of meta analysis on -Omics study

### Required Packages
shiny

### How to start the app
First, clone the project
```
git clone https://github.com/metaOmic/metaOmics
```

if the directory of the app is `metaOmics`,

* in R console
```{r eval=FALSE}
install.packages("shiny")
shiny::runApp('metaOmics', port=9987, launch.browser=T)
```

### How to start the documentation

* Install rmarkdown for R
```
install.packages("rmarkdown")
```
* Inside `doc` directory, start R console, and:
```{r eval=FALSE}
rmarkdown::run(shiny_args=list(port=9988, launch.browser=T))
```
* or in command line
```
R -e "rmarkdown::run(shiny_args=list(port=9988, launch.browser=T))"
```
* If you run into an issue with something like `pandoc version 1.12.3 or higher is required and was not found.`, just install pandoc manually. For example, on Mac, it would be `brew install pandoc`. If you have Rstudio, you can also to get rstudio's pandoc environment. Go to rstudio console and find the system environment variable for `RSTUDIO_PANDOC`
```{r eval=FALSE}
Sys.getenv("RSTUDIO_PANDOC")
```
