---
runtime: shiny
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(shiny)
library(shinyBS)
library(preproc)
source("global/constants.R")
source("global/messages.R")
source("global/help.R")
source("global/database.R")
source("global/helpers.R")
```

<script>
loading = document.createElement('div')
loading.innerHTML = '<div id="loading"><div id="loadingcontent"><p id="loadingspinner">loading......</p></div></div>'
header = document.getElementById("header")
header.insertBefore(loading, header.childNodes[0])
</script>

## sendErrorMessage(session, msg) 
`sendErrorMessage` will send a warning message to the browser, it should be used in 
`server.R` or server modules. Alternatively, we have `sendWarningMessage(session, msg)` 
`sendInfoMessage(session, msg)` and `sendSuccessMessage(session, msg)`

```{r}
# UI code
tagList(
  textInput('message', 'Enter your message', 'this is a message'),
  actionButton('errorMessage', 'Send Error Message', class="btn-danger"),
  actionButton('warningMessage', 'Send Warning Message', class="btn-warning"),
  actionButton('infoMessage', 'Send Informational Message', class="btn-info"),
  actionButton('successMessage', 'Send Success Message', class="btn-success")
)

# Server code for sending messages
observeEvent(input$errorMessage, {sendErrorMessage(session, input$message)})
observeEvent(input$warningMessage, {sendWarningMessage(session, input$message)})
observeEvent(input$infoMessage, {sendInfoMessage(session, input$message)})
observeEvent(input$successMessage, {sendSuccessMessage(session, input$message)})
```
<br />
<br />

## helpIcon(id, msg)
`helpIcon(id, msg)` will create a UI component that displays `msg` when mouse is hovered. 
Always put the definition of the message in `global/help.R` file, never enter message 
diectly. See [File Organization](file.Rmd) for more information about help message 
definition.
```{r}
# UI code
tagList( h4("Annotation"), helpIcon("annotate_help", HELP.annotate))
# UI code
tagList( h4("Delete"), helpIcon("delete_help", HELP.delete))
```
<br />
<br />

## Loading Spinner
If you have a task with long execution time, you can output a loading spinner wih some message. To start and end loading spinner, use `wait(session, msg)` and `done(session)` respectively.
```{r}
# UI code
tagList(
  textInput('loading.message', 'Enter your message', 'Loading Message....'),
  actionButton('loading.btn', 'Start a 3 second task'),
  tags$br()
)
# Server code for rendering wait and done
observeEvent(input$loading.btn, {
  wait(session, input$loading.message)
  Sys.sleep(3)
  done(session)
})
```
