---
runtime: shiny
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

The following example shows how to add a new module called `MetaXD`.

## 1. Put the module on Github.

Create a github repository to put you package.

- <b> Note the github repository name must be the same as the package name. </b>

Starting from version 0.2.0, it is required to put the supported packages on Github, as
we added a package installation interface.


## 2. Add package name to constant file
All supported packages should define its constant in `global/constants.R` file. 

- The name of the constant can be arbitrary as long as it starts with `TOOLSET.` prefix.
- The value of the constant must be the same as its package name 
  (hence github repository name). In our example it's `MetaXD`.
- Remember to both add a variable, and append it in `TOOLSET.all` vector.

So find the following section in `global/constants.R`, and insert the constant:

```{r}
# global/constants.R
TOOLSET.de    <- "MetaDE"
TOOLSET.clust <- "MetaSparseKmeans"
TOOLSET.path  <- "MetaPath"
TOOLSET.xd    <- "MetaXD" # insert this line
TOOLSET.all <- c(TOOLSET.de, TOOLSET.clust, TOOLSET.path, TOOLSET.xd) # this line is appended
```

## 3. Settings Page
Add a UI component for package in `ui/setting_ui.R`. Find the following section 
in `ui/setting_ui.R` and insert the corresping code:
```{r}
# The id of the uiOutput must be opt.packagename
tags$tbody(
  tags$tr(tags$td("Meta DE"), tags$td(uiOutput(ns("opt.MetaDE")))),
  tags$tr(tags$td("Meta Clust"), tags$td(uiOutput(ns("opt.MetaSparseKmeans")))),
  tags$tr(tags$td("Meta Path"), tags$td(uiOutput(ns("opt.MetaPath")))), # remeber to add a comma here, as it is now not the last element
  tags$tr(tags$td("Meta XD"), tags$td(uiOutput(ns("opt.MetaXD")))) # insert this line
)
```

Add a package check for your package in `server/setting_server.R` as follows:
```{r}
# First parameter is the constant we defined from step 2
# Second paramete is just a label for output log
# cran.dep is a vector of all required packages from CRAN
# bioconductor.dep is a vector of all required packages from bioconductor
check.pkg(TOOLSET.xd, 'Meta XD',
          cran.dep=c("gplots", "ggplot2", "shape"),
          bioconductor.dep=c("Biobase", "impute", "irr", "cluster", "AnnotationDbi"))

# If you are still developing the package, but you want to have a preview on setting 
# page, you can set the supported parameter to FALSE
check.pkg(TOOLSET.xd, 'Meta XD', supported=F)
```
Note this can be put anywhere, but we put them in the end of the 
`server/setting_server.R` file, so please follow convention.

<hr>
<center> Congratulations! Now you should be able to test it, and see if 
setting page behave as expected </center>
<hr>

## 4. UI Module
First you need to create a skeleton for the ui module, and then calls the module 
in `ui.R`. The following serves as and example for `Meta XD` UI module:
```{r}
# This is ui/meta_xd_ui.R
# UI module is essentially just a function that return UI component
# By convention, the name of this function is the name of the package 
# being snake cased, and appended by _ui.R
meta_xd_ui <- function(id, label = "meta XD") {
  ns <- NS(id)
  # This "Meta XD" is the what appears in Menu. It does not have to be the same
  # as package name, it can be a more readable word
  tabPanel("Meta XD", value=id,
    sidebarLayout(
      # sidebarPanel by default will occupy left one third of the width
      sidebarPanel(
        # Put all your options/settings here
	tags$hr(),
        # Usually you have a button called "run"
        actionButton(ns('run'), 'Run', icon=icon("rocket"), class="btn-success btn-run")
      ),
      # sidebarPanel by default will occupy right two third of the width
      mainPanel(
        # Put your result display here
      )
    )
  )
}
```

With the above `ui/meta_xd_ui.R`, we should call it in `ui.R`. Find below section in `ui.R` and insert necessary code as follows:
```{r}
toolsets <- c("Toolsets")
if (TOOLSET.de %in% enabled)
  toolsets <- c(toolsets, list(meta_de_ui("meta_de")))
if (TOOLSET.clust %in% enabled)
  toolsets <- c(toolsets, list(meta_clust_ui("meta_clust")))
if (TOOLSET.path %in% enabled)
  toolsets <- c(toolsets, list(meta_path_ui("meta_path")))
# insert these following two lines
# What it does is simply calling the meta_xd_ui function we just created with a
# unique ID that will serve to distinguish the name space of different UI module
if (TOOLSET.xd %in% enabled)
  toolsets <- c(toolsets, list(meta_xd_ui("meta_path")))

```

<hr>
<center> Congratulations! Now you should be able to test it, and see if 
there is an extra button under the Toolsets menu that link to your ui page</center>
<hr>

## 5. Server Module
First you need to create a skeleton for the server module, and then calls the module 
in `server.R`. The following serves as and example for `Meta XD` server module:
```{r}
meta_xd_server <- function(input, output, session) {
  # The library of your package is included here, as it is only relevent
  # this server module
  library(MetaDE)

  # This create a namespace function called ns, and we will call ns on all ids
  ns <- NS("meta_de")

  # Trust me, steps for obtaining options in sidebarPanel can be really complicated!
  # It is wise to create a function that get our option from input as a named list
  getOption <- function(input) {
    # initialize the list
    opt <- list()
    # some imaginary codes that handle complicated option logic
    opt$A <- input$A
    if (input$A == 0)
      opt$B <- input$B
    else
      opt$C <- input$C
    # return this option
    opt
  }

  ##########################
  # Reactive Values        #
  ##########################
  # This is the section where you set all the custom reactive values needed
  # It is common to let the current active study to be a reactive value
  # as our options and result often depends on the active study
  DB <- reactiveValues(active=DB.load.active(db))

  ##########################
  # Validation             #
  ##########################
  # Write your complicated validation function here. Refer to 
  # Helpers -> Exception Handling
  # on how to use this validators with Try block
  validate <- function() {
    if(length(DB$active) == 0 )
      warning(MSG.no.active)
  }

  ##########################
  # Observers              #
  ##########################
  # All observers go in here

  # This is a very common observer that observes the event of tab change.
  # And usually it resets the DB$active to the current active study, so that
  # other ui components and change with respect to DB$active (as it is a reactive value)
  observeEvent(input$tabChange, {
    DB$active <- DB.load.active(db)
  })

  # An example observer for the input run button
  observeEvent(input$run, {
    wait(session, "running meta XD, should be soon")
    try({
      do.call(MetaXD, getOption(input))
    }, session)
    done(session)
  })

  ##########################
  # Render output/UI       #
  ##########################
  # This is where you render UI to the dynamic UI component

  output$someUIOutput <- renderUI({
    # Some UI component
  })

  output$someTextOutput <- renderText({
    # Some text messages
  })
}
```

With the above `server/meta_xd_server.R`, we should call it in `server.R`. Find below section in `server.R` and insert necessary code as follows:
```{r}
if (TOOLSET.de %in% installed)
  callModule(meta_de_server, "meta_de")
if (TOOLSET.clust %in% installed)
  callModule(meta_clust_server, "meta_clust")
if (TOOLSET.path %in% installed)
  callModule(meta_path_server, "meta_path")
# Insert the following two lines
# The first parameter of callModule is the module function we just defined in
# meta_xd_server.R
# The second parameter of the callModule is the same as the id used to call the
# meta_xd_ui module
if (TOOLSET.xd %in% installed)
  callModule(meta_path_server, "meta_path")
```
<hr>
<center> Congratulations! Now you have done everything necessary to creata a module. 
</center>
<center>
From now on, all is left to do is keep developing the `ui/meta_xd_ui.R` and 
`server/meta_xd_server.R` </center>
<hr>
